SpARC: Sparse Redundant Calibration

### 2016-07-12 paper.tex
made little progress with complex optimization section

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Complex Optimization}
The most standard way of tackling the calibration problem is to treat the real and imaginary parts of the residual (difference between observed and predicted visibilities) separately and then to simultaneously solve for the real and imaginary parts
of the gains. \citet{Smirnov2015} have recently shown that calibration can be performed using a complex optimization framework. The main difference between the traditional approach and the 
complex optimization framework proposed by \citet{Smirnov2015} is that in their framework they no longer treat the real and imaginary parts of the residual separately which enables them to directly solve for the complex antenna gains themselves (as well as their
complex conjugates). Recall that most optimization techniques require a gradient operator to enable it to function properly. The main reason why we have traditionally treated 
the real and imaginary parts of the residual separately is due to the fact that $f(z) = \conj{z}$ is not a differentiable complex function where $z\in\mathbb{C}$ and $\conj{(*)}$ denotes conjugation, i.e. $\frac{df(z)}{dz}$
does not exist, if we apply the standard definition of differentiation:
\begin{equation}
x
\end{equation}

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Complex Optimization}
Scalar direction independent calibration is achieved through solving the following minimization problem:
\begin{equation}
\min_{\bg}\|\br\| = \min_{\bg}\|\bd - \bv(\bg)\|, 
\end{equation}
where
\begin{enumerate}
 \item $\bd$ is the observed visibility vector, i.e. 
 \begin{equation}
  \bd = [d_{pq}] \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 The vector entry $d_{pq}$ denotes the observed visibility associated with the baseline formed by antenna $p$ and $q$, while $N$ denotes the number or antennas
 in the array. 
 \item $\bg = [g_1,g_2,\cdots,g_N]$ represents the instrumental complex antenna gain vector.
 \item $\bv(\bg)$ denotes the predicted visibility vector, i.e.
 \begin{equation}
  \bv(\bg) = [g_p y_{pq}\conj{g}_q]  \big \} ~ [pq] = 1\cdots N ~ (p<q).
 \end{equation}
 In Eq... $y_{pq}$ denotes the synthetic visibility which was generated by

\end{enumerate}

The most standard way of tackling the calibration problem is to treat the real and imaginary parts of the residual (difference between observed and predicted visibilities) separately and then to simultaneously solve for the real and imaginary parts
of the gains. \citet{Smirnov2015} have recently shown that calibration can be performed using a complex optimization framework. The main difference between the traditional approach and the 
complex optimization framework proposed by \citet{Smirnov2015} is that in their framework they no longer treat the real and imaginary parts of the residual separately which enables them to directly solve for the complex antenna gains themselves (as well as their
complex conjugates). Recall that most optimization techniques require a gradient operator to enable it to function properly. The main reason why we have traditionally treated 
the real and imaginary parts of the residual separately is due to the fact that $f(z) = \conj{z}$ is not a differentiable complex function where $z\in\mathbb{C}$ and $\conj{(*)}$ denotes conjugation, i.e. $\frac{df(z)}{dz}$
does not exist, if we apply the standard definition of differentiation:
\begin{equation}
x
\end{equation}
